\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-07 paper/relatedwork.tex
removed references to SimpleDB, clarified some stuff, and added TODOs
paper: added timeseries forecasting related work

>>>>

\subsection{Forecasting and Databases}
\cite{parisi2011embedding} introduces the idea of incorporating time-series forecast operators into
databases, along with the necessary relational algebra extensions. Their work explores the theoretical
properties of forecast operators and generalizes them into a family of operators, distinguished by
the type of predictions returned. They highlight the use of forecasting for replacing missing values.
In their follow on work\cite{parisi2013temporal}, they identify various equivalence and containment
relationships when using forecast operators, which could be used to perform query plan transformations that guarantee the same result. They
explore forecast-first and forecast-last plans, which perform forecasting operations before and after traditional
relational operators, respectively.

In contrast to this work, \ProjectName{} is targeted at generic value imputation, not necessarily tailored to 
time-series. The optimizer is not based on equivalence transformations, nor are there guarantees of equal
results under different conditions. Instead, the optimizer allows users to pick their tradeoff between
runtime cost and information loss. The search space considered by our optimizer is broader, not just
forecast-first/forecast-last plans, but rather imputation operators can be placed anywhere in the query plan
(with some restrictions). The novelty of our contribution lies in the successful incorporation of
imputation operations in non-trivial query plans with cost-based optimization.

\cite{duan2007processing} describes the Fa system and its declarative language for time-series forecasting. Their
system automatically searches the space of attribute combinations/transformations and statistical models
to produce forecasts within a given accuracy threshold. Accuracy estimates are determined using
standard techniques, such as k-fold cross-validation.

\ProjectName{} provides a declarative language, as
an extension to standard SQL, but in contrast to Fa, \ProjectName{} is not searching the space of possible
imputation models, but rather the space of query plans that incorporate imputation operators. Another major point
of distinction between \ProjectName{} and Fa is that the latter doesn't consider tradeoffs between accuracy and computation time, 
but rather returns the most accurate forecast (with some stopping criterion).
